### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@8d51cc2b20940e8fef109e7a46befa7c19c71f4a 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@f8a80127fd198dec6d1cd3171e9af8a62b142f0e 🚀

\geometry{includemp,
            letterpaper,
            top=1.0in,
            bottom=2.510cm,
            left=0.35in,
            right=0.35in,
            marginparwidth=2.0in,
            marginparsep=0.35in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}
\usepackage{floatrow}
\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}
\floatsetup[table]{margins=hangright,
             facing=no,
             capposition=beside,
             capbesideposition={center,outside},
             floatwidth=\textwidth}

>>>>

\geometry{includemp,
            letterpaper,
            top=2.4cm,
            bottom=2.4cm,
            left=1.0cm,
            right=1.0cm,
            marginparwidth=5cm,
            marginparsep=1.0cm}

\usepackage[singlelinecheck=off]{caption}

\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}

\usepackage{floatrow}

\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}

% \floatsetup[table]{margins=hangright,
%              facing=no,
%              capposition=beside,
%              capbesideposition={center,outside},
%              floatwidth=\textwidth}
